Lock-free Skiplist-based Priority Queues \\ Student Paper for Seminar in Algorithms 2013W \\ Technical University of Vienna

### 2014-03-13 paper/paper.tex
Initial Wimmer paragraphs

The body of work discussed in previous sections
creates the impression that limits of strict, deterministic priority queues have been reached.
In particular, \citeauthor{} conclude that scalability is solely limited by \lstinline|DeleteMin|,
and that less than one modified memory location per thread and operation would have to be read
in order to achieve improved performance \cite{}. % TODO: Cites for this entire section.

@@

Relaxation has also been applied to concurrent priority queues with some success, and in the following
sections we discuss two different approaches.

\subsection{Wimmer} \label{sec:wimmer}
\subsection{SprayList} \label{sec:spraylist}

>>>>

The body of work discussed in previous sections
creates the impression that limits of strict, deterministic priority queues have been reached.
In particular, \citeauthor{linden2013skiplist} conclude that scalability is solely limited by \lstinline|DeleteMin|,
and that less than one modified memory location per thread and operation would have to be read
in order to achieve improved performance \cite{linden2013skiplist}. % TODO: Cites for this entire section.

@@

Relaxation has also been applied to concurrent priority queues with some success, and in the following
sections we discuss two such approaches.

\subsection{Wimmer} \label{sec:wimmer}

\citeauthor{wimmer2013data} presented the first relaxed, linearizable, and lock-free priority queue
in \cite{wimmer2013data}. An open-source implementation is available in the task-scheduling system
\emph{Pheet}\footnote{\url{http://pheet.org}}.

The \citeauthor{wimmer2013data} priority queue was evaluated using a label-correcting variant
of Dijkstra's shortest path algorithm \cite{}. Their model creates a task for each node
expansion, and therefore comes with a considerable task scheduling overhead. Nonetheless,
the parallel implementation scales well up to 10 threads, and further limited performance
gains are made until 40 threads. To date, no direct comparisons to other concurrent
priority queues have been possible since the data structure is strongly tied to \emph{Pheet},
but a separate implementation of k-priority queues is planned.

\subsection{SprayList} \label{sec:spraylist}
